Design and Implementation of Probabilistic Programming Language Anglican

### 2016-08-08 paper/paper.tex
update
minor

\newcommand*{\dt}[1]{{ \bf [}{\bf DT:} {\it #1}{\bf ]}}
\newcommand*{\fw}[1]{{ \bf [}{\bf FW:} {\it #1}{\bf ]}}
\newcommand*{\hy}[1]{{ \bf [}{\bf HY:} {\it #1}{\bf ]}}
\newcommand*{\jw}[1]{{ \bf [}{\bf JW:} {\it #1}{\bf ]}}

@@

\hy{I found this section confusing in the following sense. First,
it does not highlight the most interesting aspects of the compilation
of Anglican. It gives a good overview on how the compilation is
implemented, but a reader might want to see something unique and
interesting about Anglican. To me, the most interesting part of the
compilation is the treatment of probabilistic constructs in Anglican's
CPS transformation. How are sample,
observe and stochastic memoization compiled? How should the standard
CPS transformation be modified in order to handle these constructs?
The use of state can be one answer for the second question.
The second most interesting part is about the use of trampolining
the mix with Clojure code.

Second, the section assumes that a reader is already familiar 
with Clojure or something specific to probabilistic programming. For 
instance, it might be that a reader  has never heard about
Clojure records and stochastic memoization. Then, she or he
would have difficulties in following this section.

What should we do? One option is not to do anything. Another is
to take care of the second point. That is, we make the section
easily followed by someone who does not know Clojure. The third
is to restructure the section and to take care of my first criticism.}

@@

The sole purpose of the algorithm identifier is method dispatch
--- conventionally, the identifier is a keyword related to the
algorithm name (\texttt{:lmh} for Lightweight
Metropolis-Hasting, \texttt{:pcascade} for Particle Cascade
etc.). The second parameter is a query as defined by
\texttt{query} or \texttt{defquery} forms. If needed, the query
can be defined anonymously, right in the argument list of a call
to \texttt{infer}:
\begin{lstlisting}[style=default]
(let [x 1]
  (infer :pgibbs (query (predict x)) nil))
\end{lstlisting}
A query is executed by calling the initial continuation of the
query, which accepts a value and a state. The state is supplied
by the inference algorithm, however the value is provided as a
parameter of \texttt{infer}. A query does not have to have any
parameters, in which case the value can be simply \texttt{nil}.
When a query is defined with a binding for the initial value,
the value becomes available inside the query. The value is
destructured in case of a structured binding, for example:
\begin{lstlisting}[style=default]
(defquery my-query [mean sd]
  (predict (sample (normal mean sd))))

(def samples (infer :lmh my-query [1.0 3.0]))
\end{lstlisting}
Finally, an indefinite number of auxiliary arguments can be
passed to \texttt{infer}. By convention, the arguments should be
keyword arguments, and are interpreted in the algorithm-specific
manner.

>>>>

\newcommand*{\dt}[1]{\smallskip\noindent\fbox{\begin{minipage}{\linewidth}{\bf DT:} 
        {\rm #1}\end{minipage}}}
\newcommand*{\fw}[1]{\smallskip\noindent\fbox{\begin{minipage}{\linewidth}{\bf FW:} 
        {\rm #1}\end{minipage}}}
\newcommand*{\hy}[1]{\smallskip\noindent\fbox{\begin{minipage}{\linewidth}{\bf HY:} 
        {\rm #1}\end{minipage}}}
\newcommand*{\jw}[1]{\smallskip\noindent\fbox{\begin{minipage}{\linewidth}{\bf JW:} 
        {\rm #1}\end{minipage}}}

@@

\hy{I found this section confusing in the following sense. First,
it does not highlight the most interesting aspects of the compilation
of Anglican. It gives a good overview on how the compilation is
implemented, but a reader might want to see something unique and
interesting about Anglican. To me, the most interesting part of the
compilation is the treatment of probabilistic constructs in Anglican's
CPS transformation. How are sample,
observe and stochastic memoization compiled? How should the standard
CPS transformation be modified in order to handle these constructs?
The use of state can be one answer for the second question.
The second most interesting part is about the use of trampolining
the mix with Clojure code.
Second, the section assumes that a reader is already familiar 
with Clojure or something specific to probabilistic programming. For 
instance, it might be that a reader  has never heard about
Clojure records and stochastic memoization. Then, she or he
would have difficulties in following this section. 
What should we do? One option is not to do anything. Another is
to take care of the second point. That is, we make the section
easily followed by someone who does not know Clojure. The third
is to restructure the section and to take care of my first criticism.}

@@

The sole purpose of the algorithm identifier is method dispatch
--- conventionally, the identifier is a keyword related to the
algorithm name (\texttt{:lmh} for Lightweight
Metropolis-Hasting, \texttt{:pcascade} for Particle Cascade
etc.). The second parameter is a query as defined by
\texttt{query} or \texttt{defquery} forms. If needed, the query
can be defined anonymously, right in the argument list of a call
to \texttt{infer}:
\begin{lstlisting}[style=default]
(let [x 1]
  (infer :pgibbs (query (predict x)) nil))
\end{lstlisting}
A query is executed by calling the initial continuation of the
query, which accepts a value and a state. The state is supplied
by the inference algorithm, while the value is provided as a
parameter of \texttt{infer}. A query does not have to have any
parameters, in which case the value can be simply \texttt{nil}.
When a query is defined with a binding for the initial value,
the value becomes available inside the query. A query may
accept multiple parameters as components of a Clojure vector,
in which case the initial value is given as a vector and its
components get bound to the corresponding parameters of the
query (via destructuring).
%The value is destructured via pattern match in case of a structured binding. 
For example,
\begin{lstlisting}[style=default]
(defquery my-query [mean sd]
  (predict (sample (normal mean sd))))

(def samples (infer :lmh my-query [1.0 3.0]))
\end{lstlisting}
Finally, any number of auxiliary arguments can be
passed to \texttt{infer}. 
%Finally, an indefinite number of auxiliary arguments can be
%passed to \texttt{infer}. 
By convention, the arguments should be
keyword arguments, and are interpreted in the algorithm-specific
manner.
